Transitivity of Subtyping for Intersection Types

### 2020-05-15 papers/LMCS-subtyping-intersections/paper.tex
check

Intersection types were invented by Coppo, Dezani-Ciancaglini, and
Salle to study normalization in the lambda
calculus~\citep{Coppo:1979aa}. Subsequently intersection types have
been used for at least three purposes:
\begin{enumerate}
  \item in type systems for programming
    languages~\citep{Reynolds:1988aa,Pierce:1991aa,Castagna:2014aa,Chaudhuri:2014aa,Oliveira:2016aa,Amin:2017aa,Muehlboeck:2018aa,Bi:2019aa,Dunfield:2019aa,Microsoft:TypeScript2020aa,Dotty:2020aa},
  \item in precise static
    analyses~\citep{Turbak:1997aa,Palsberg:1998aa,Mossin:2003aa,Simoes:2007aa},
    and
  \item in filter models for the denotational semantics of a variety
    of lambda
    calculi~\citep{Coppo:1980ab,Coppo:1981aa,Coppo:1984aa,Honsell:1992aa,Abramsky:1993fk,Honsell:1999aa,Ishihara:2002aa,Rocca:2004aa,Dezani-Ciancaglini:2005aa,Alessi:2006aa,Barendregt:2013aa}.
\end{enumerate}
The motivation for this article comes from the third use of
intersection types, in denotational semantics.  We are interested in
constructing filter models for functional programming languages in
support of mechanized compiler
verification. Section~\ref{sec:motivation} describes how that research
motivates the results in this article.

@@

\section{Transitivity}
\label{sec:trans}

>>>>

Intersection types were invented by Coppo, Dezani-Ciancaglini, and
Salle to study normalization in the lambda
calculus~\citep{Coppo:1979aa}. Subsequently intersection types have
been used for at least three purposes:
\begin{enumerate}
  \item in type systems for programming
    languages~\citep{Reynolds:1988aa,Pierce:1991aa,Castagna:2014aa,Chaudhuri:2014aa,Oliveira:2016aa,Amin:2017aa,Muehlboeck:2018aa,Bi:2019aa,Dunfield:2019aa,Microsoft:TypeScript2020aa},
  \item in precise static
    analyses~\citep{Turbak:1997aa,Palsberg:1998aa,Mossin:2003aa,Simoes:2007aa},
    and
  \item in filter models for the denotational semantics of a variety
    of lambda
    calculi~\citep{Coppo:1980ab,Coppo:1981aa,Coppo:1984aa,Honsell:1992aa,Abramsky:1993fk,Honsell:1999aa,Ishihara:2002aa,Rocca:2004aa,Dezani-Ciancaglini:2005aa,Alessi:2006aa,Barendregt:2013aa}.
\end{enumerate}
The motivation for this article comes from the third use of
intersection types, in denotational semantics.  We are interested in
constructing filter models for functional programming languages in
support of mechanized compiler
verification. Section~\ref{sec:motivation} describes how that research
motivates the results in this article.

@@

\section{Proof of Transitivity of Subtyping}
\label{sec:trans}
